---
title: "HW4"
author: "Lafaith Allen-Delice"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
---

```{r setup, include=FALSE}
library(flexdashboard) # always
```

Intro {.sidebar}
=====================================
This dashboard contains five visualizations using datasets related to arrests, COVID-19 statistics, and city safety indicators. The first graph is a bar chart displaying the Arrests by Sex and Race. The second graph is a histogram displaying the distribution of student enrollment across Massachusetts schools. The data is from the NCES Massachusetts school excel datasheet. The second graph is a histogram displaying the distribution of student enrollment across Massachusetts schools.  The third graph is a histogram displaying the distribution of student enrollment across Massachusetts schools. The third graph is a histogram displaying the distribution of student enrollment across Massachusetts schools. 


References: {.tabset .tabset-fade}
=====================================
The following data sets were used: 

https://github.com/lallen-student/HW4/blob/main/Mass_Arrests.xlsx
https://github.com/lallen-student/HW4/blob/main/covid-19.csv
https://github.com/lallen-student/HW4/blob/main/safeCities_ecoUI.xlsx

Arrests by Sex and Race {.tabset .tabset-fade}
=====================================

```{r}
## for del1Draft.rds
link1a="https://github.com/lallen-student/HW4/raw/main/del1Draft.rds"
readRDS(url(link1a))
```

Daily Cases vs. Daily Deaths {.tabset .tabset-fade}
====================================

```{r}
## for del2Draft.rds
link2a="https://github.com/lallen-student/HW4/raw/main/del2Draft.rds"
readRDS(url(link2a))
```

Arrests by Race and Age {.tabset .tabset-fade}
=====================================

```{r}
## for del3Draft.rds
link3a="https://github.com/lallen-student/HW4/raw/main/del3Draft.rds"
readRDS(url(link3a))
```

Old Heat Map {.tabset .tabset-fade}
=====================================

```{r}
## for del4Draft.rds
link4a= "https://github.com/lallen-student/HW4/raw/main/del4Draft.rds"
readRDS(url(link4a))
```


Improved Heat Map {.tabset .tabset-fade}
=====================================

```{r}
## for del5Draft.rds
link5a= "https://github.com/lallen-student/HW4/raw/main/del5Draft.rds"
readRDS(url(link5a))
```
