---
title: "HW4"
author: "Lafaith Allen-Delice"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
---

```{r setup, include=FALSE}
library(flexdashboard) # always
```

# Intro {.sidebar}

### Brief Description

This dashboard contains five visualizations using data sets related to arrests, COVID-19 statistics, and city safety indicators.

### Visualization Descriptions

This dashboard contains five visualizations using datasets related to arrests, COVID-19 statistics, and city safety indicators.

- The first graph is a bar chart displaying arrests by sex and race using the Mass_Arrests.xlsx dataset.

- The second graph is a scatterplot showing average daily COVID-19 cases and average daily deaths using the covid-19.csv dataset.

- The third graph is a boxplot displaying the distribution of age across racial groups using the Mass_Arrests.xlsx dataset.

- The fourth graph is a copy of the provided heatmap using the safeCities_ecoUI.xlsx dataset.

- The fifth graph is an improved version of that heatmap.

Links to the datasets are available in the References tab.

# References: {.tabset .tabset-fade}

### Links

The following data sets were used:

- <https://github.com/lallen-student/HW4/blob/main/Mass_Arrests.xlsx> 
- <https://github.com/lallen-student/HW4/blob/main/covid-19.csv> 
- <https://github.com/lallen-student/HW4/blob/main/safeCities_ecoUI.xlsx>

# Arrests by Sex and Race {.tabset .tabset-fade}

### Arrests by Sex and Race

```{r}
## for del1Draft.rds
link1a="https://github.com/lallen-student/HW4/raw/main/del1Draft.rds"
readRDS(url(link1a))
```

# Daily Cases vs. Daily Deaths {.tabset .tabset-fade}

### Average daily COVID-19 cases and average daily deaths

```{r}
## for del2Draft.rds
link2a="https://github.com/lallen-student/HW4/raw/main/del2Draft.rds"
readRDS(url(link2a))
```

# Arrests by Race and Age {.tabset .tabset-fade}

### Distribution of age across racial groups

```{r}
## for del3Draft.rds
link3a="https://github.com/lallen-student/HW4/raw/main/del3Draft.rds"
readRDS(url(link3a))
```

# Old HeatMap {.tabset .tabset-fade}

### Provided Heatmap

```{r}
## for del4Draft.rds
link4a= "https://github.com/lallen-student/HW4/raw/main/del4Draft.rds"
readRDS(url(link4a))
```

# Improved Heat Map {.tabset .tabset-fade}

### Average Safety Scores by City and Dimension {data-width="450"}

```{r, fig.width=10, fig.height=14}

## for del5Draft.rds
link5a= "https://github.com/lallen-student/HW4/raw/main/del5Draft.rds"
readRDS(url(link5a))
```

